Mohammadmahdi Maghouli
 (+1)825-333-1369 |  maghouli@ualberta.ca |  mmahdim77 |  mmahdim
Summary
Passionate and highly skilled Applied Machine Learning researcher with 4 years of experience in AI
software development, specializing in robust deep learning models for multi-agent systems. Proficient
in Python and deep learning frameworks like PyTorch and TensorFlow, with experience in tuning
deep learning algorithms. Deep understanding of neural networks, large language models (LLMs),
and AI systems development. Demonstrated strong problem-solving, analytical skills, and teamwork
abilities within agile environments. Dedicated to applying AI research to real-world problems and
driving innovation in game theory and artificial intelligence to make a meaningful impact.
Education
MSc, Computing Science (GPA:3.9/4) Edmonton, Alberta
University of Alberta Sep.2022 - Exp. Grad: Dec.2024
• Thesis Title: Incentivizing Virtual Power Plant Participation via Shapley Value Rewards.
Supervisor: James Wright 
Bachelor of Science, Computer Engineering (GPA:3.54/4) Tehran, Iran
Shahid Beheshti University Sep. 2017 - Jan. 2021
• Thesis:Obfuscated Malware Detection via Contrastive Learning with a Semi-Supervised Approach
Work Experieces
Aalto University | Machine Learning Research Intern Helsinki, Finland
INDECS Project Jun. 2024 - Sep 2024
• Developed a deep reinforcement learning model to optimize HVAC electricity consumption on
cruise ships, reducing simulated energy usage by 20% as part of the INDECS project in collabora-
tion with Royal Caribbean  (Python, Pytorch, APROS).
• Collaborated cross-functionally with domain experts to model complex HVAC systems for cruise
ships and vertical farms using the APROS simulator.
PoScout | Product Manager and ML Researcher Edmonton, Alberta
Startup Aug. 2023 - May 2024
• Led the development of an LLM-based student-professor matching platform, successfully coordi-
nating a cross-functional team of ML scientists, engineers, and business stakeholders to deploy a
production-ready solution.
• Developed and deployed a prompt evaluation framework, improving document generation quality
through iterative prompt engineering, A/B testing, and metric-driven optimization (OpenAI APIs,
Python, Tensorflow, GCP).
Chaos | Applied Machine Learning Scientist Tehran, Iran
Startup Jan. 2022 - Jan 2023
• Collaborated with a team of four ML engineers to develop and launch a FinTech portfolio manage-
ment platform, achieving a 30%+ improvement in portfolio returns through deep reinforcement
learning techniques (TensorFlow, Python).
Astute Vision |Machine Learning Engineer London, United Kingdom
Startup Apr. 2020 - Dec. 2022
• Pioneered the implementation of a new hierarchical, large-scale object detection model capable of
classifying over 50,000 types of items in grocery store shelf images with 93% accuracy.
• Mastered software engineering and object-oriented programming through the development of an
innovative AI-backed commercial inventory management software, incorporating cutting-edge
shelf image analysis from initial concept to completion.
LAST UPDATED: APRiL 28, 2025 MOHAMMAD MAHDi MAGHOULi · RÉSUMÉ 1 / 2
Work Integrated Learning Opportunities
Amii | Technical Advisement - AI Planning and Initiation (AIPI) Edmonton, Alberta
Feb. 2024 - May 2024
• Facilitated breakout room discussions and guided conversations during client workshops, con-
tributing to the development of materials that support workshop activities and future WILO deliv-
eries in AIPIs, ensuring clients could identify problem areas and potential ML approaches.
• Conducted comprehensive research on client organizations and potential use cases to support
the Industry Team, enhancing the effectiveness of AIPI Sessions aimed at identifying business
opportunities for ML applications.
Amii | Technical Consultant and Client Success Coach Edmonton, Alberta
Jul. 2023 - Dec 2023
• Showcased strong foundational knowledge in ML through the development of both practical and
theoretical solutions across various domains such as reinforcement learning, computer vision, and
natural language processing, addressing complex open-ended problems effectively.
• Enhanced consultation and critical thinking skills through advising multiple Business CTOs in
diverse industries such as food, retail, utilities, and agriculture, focusing on optimizing their AI-
driven solutions.
• Honed my report writing and note taking skills by actively engaged in weekly meetings, focusing
on meticulous documentation of brainstormed ideas and information.
Amii | Content Development Support - Case Studies | AI Ethics,
Regulations, and AI applications in Utilities Edmonton, Alberta
Jul. 2023 - Dec 2023
• Developed educational content on AI regulations and ethics, showcasing the potential of AI in
utilities, emphasizing continuous learning and agile methodologies.
• Collaborated with a diverse group of Machine Learning Educators to curate and update resources
that addressed emerging technologies and discoveries in AI, ensuring that materials were accessi-
ble and relevant to a broad audience.
Business Case Competition - Second Place Edmonton, Alberta
Business Technology Management Club (BTMC), University of Alberta Jan 2024
• Secured the 2nd place among 30 teams in a challenging business case competition.
• Recognized for exceptional communication and presentation skills, receiving positive feedback for
slide quality, confidence, and overall team energy.
• Demonstrated adeptness in problem-solving and strategic thinking during Q & A sessions, further
highlighting strong communication capabilities.
Publications
[1] Maghouli, Mohammad Mahdi , Sarikonda, Jashwanth Reddy, Ardakanian, Omid. “HeteroFed:
Heterogeneous Federated Learning with the help of Model Distillation ,” in press.
[2] Maghouli, Mohammad Mahdi, et al. “Malfustection: Obfuscated Malware Detection and Mal-
ware Classification with Data Shortage by Combining Semi-Supervised and Contrastive Learn-
ing.” arXiv preprint, arXiv:2111.09975 (2022). [Link]